\documentclass[preprint2]{aastex62}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\usepackage{amsmath}
\usepackage{cancel}
\usepackage{float}

\shorttitle{Updated Opacities for DSEP}
\shortauthors{Boudreaux et al.}
% \watermark{DRAFT}
% \graphicspath{{./}{figures/}{src/figures}}

\begin{document}

\title{Updated High-Temperature Opacities for The Dartmouth Stellar Evolution
Program and their Effect on the Jao Gap Location}

\correspondingauthor{Thomas M. Boudreaux}
\email{thomas.m.boudreaux.gr@dartmouth.edu,\\thomas@boudreauxmail.com}

\author[0000-0002-2600-7513]{Thomas M. Boudreaux}
\affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}

\author[0000-0003-3096-4161]{Brian C. Chaboyer}
\affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}

\received{9/20/2022}
\revised{12/12/2022}
\revised{1/23/2023}
\accepted{1/24/2023}
% \submitjournal{ApJ}


\begin{abstract}

	The Jao Gap, a 17 percent decrease in stellar density at M$_{G} \sim$ 10
	identified in both Gaia DR2 and EDR3 data, presents a new method to probe
	the interior structure of stars near the fully convective transition mass.
	The Gap is believed to originate from convective kissing instability
	wherein asymmetric production of $^{3}$He causes the core convective zone
	of a star to periodically expand and contract and consequently the stars’
	luminosity to vary. Modeling of the Gap has revealed a sensitivity in its
	magnitude to a population’s metallicity primarily through opacity. Thus
	far, models of the Jao Gap have relied on OPAL high-temperature radiative
	opacities. Here we present updated synthetic population models tracing the
	Gap location modeled with the Dartmouth stellar evolution code using the
	OPLIB high-temperature radiative opacities. Use of these updated opacities
	changes the predicted location of the Jao Gap by $\sim$0.05 mag as compared
	to models which use the OPAL opacities. This difference is likeley too
	small to be detectable in empirical data.

\end{abstract}

\keywords{Stellar Evolution (1599) --- Stellar Evolutionary Models (2046)}

\input{intro.tex}

\input{JaoGap.tex}

\input{opacity.tex}

% \input{SSCM.tex}

\input{Modeling.tex}

\input{Results.tex}

\input{Conclusion.tex}



\acknowledgments{
	This work has made use of the NASA astrophysical data system (ADS). We
	would like to thank Elisabeth Newton, Aaron Dotter, and Gregory Feiden for
	their support and for useful discussion related to the topic of this paper.
	We would like to thank our reviewer for their critical eye and their
	guidance to investigate to effects of the mixing length on the Gap
	Location. Additionally, we would like to thank James Colgan and the Los
	Alamos T-1 group for their assistance with the OPLIB opacity tables and
	support for the public release of \texttt{pyTOPSScrape}. We acknowledge the
	support of a NASA grant (No. 80NSSC18K0634). 
}
\acknowledgments

% \begin{acknowledgments}
% 	This work has made use of the NASA astrophysical data system (ADS). We
% 	would like to thank Elisabeth Newton, Aaron Dotter, and Gregory Feiden for
% 	their support and for useful discussion related to the topic of this paper.
% 	We would like to thank our reviewer for their critical eye and their
% 	guidance to investigate to effects of the mixing length on the Gap
% 	Location. Additionally, we would like to thank James Colgan and the Los
% 	Alamos T-1 group for their assistance with the OPLIB opacity tables and
% 	support for the public release of \texttt{pyTOPSScrape}. We acknowledge the
% 	support of a NASA grant (No. 80NSSC18K0634). 
% \end{acknowledgments}

\software{
	The Dartmouth Stellar Evolution Program (DSEP) \citep{Dotter2008},
	\texttt{BeautifulSoup} \citep{richardson2007beautiful},
	\texttt{mechanize} \citep{chandra2015python},
	\texttt{FreeEOS} \citep{Irwin2012},
	\texttt{pyTOPSScrape} \citep{Boudreaux22}
}

\appendix

\input{pytopsscrape.tex}

\input{interp.tex}



\bibliography{ms}{}
\bibliographystyle{aasjournal}


\end{document}

