The red giant branch bump (RGBB) is a feature experienced by many stars as they
ascend the RGB \citep{Riello2003}. During this period, as the core of the star
is contracting and heating the surronding matierial shell burning begins.
Regions of the star which were previously too cool to fuse hydrogesn (and so
therefore still have hydrogen fuel despite core depletion) begin to fuse. At
the same time, because of the increase energy output from the heating core and
shell burning the balance between the adiabatic and radiative temperature
gradients near the convective envlope of the star begins to flip. This results
in the convective envelope pushing deeper --- in mass fraction --- into the
star. As the convective envelope reaches further into the star hydrogen from
the stars outer layers may be effeciently mixed deeper. The convective envelope
only ever manages to reach a fraction of a stars mass fraction during this
phase of evolution; however, due to the efficient mixing, by the time it starts
to recede to the surface there is a radial discontinuity in the hyrdogen
concentration within the star. If shell burning reaches this far out then the
normal corse of RGB asension will be interupted by an anoumously large amount
of fuel. The star will remain burning that shell for longer than might
otherwise be predicted leading to a ``bump'' in the luminosity function. This
is known as the Red Giant Branch Bump.

The RGBB provides yet another view into the interior physics of a star and may
allow for calibration and testing of stellar models against observations.
Previous work by \citet{Joyce2016} has found that current
generation 1D stellar models, such as DSEP, may undersestimate the bump
luminosity for metal poor stars but that they generally models the bump well
for more metal rich stars.

In this chapter we will provide two breif views into the RGBB. First, we will
look at how different self consistent models of multiple populations in NGC
2808 (the same models disscused in Chapter \ref{chap:ngc2808}) effect the
RGBB location. Second, we will investigate how the updated low and high
temperature opacities which we have incorperated into DSEP effect the RGBB
location.
