\section{Stellar Models}\label{sec:modeling}
We use the Dartmouth Stellar Evolution Program \citep[DSEP, ][]{Dotter2008} to
generate stellar models. DSEP is a well-tested, one-dimensional stellar
evolution code which includes a mixing length model of convection,
gravitational settling, and diffusion. Using the solar composition presented in
\citep{Grevesse2007} (GAS07), MARCS model atmosphers, OPLIB high temperature
opacities, and AESOPUS 2.0 low temperautre opacities we find a solar calibrated
mixing length parameter, $\alpha_{MLT}$, of $\alpha_{MLT} = 1.901$.

We use DSEP to evolve stellar models ranging in mass from 0.3 to 2.0 solar
masses from the zero-age main sequence (ZAMS) to the tip of the red giant
branch. Below 0.7 $M_{\odot}$ we evolve a model every 0.03 $M_{\odot}$ and
above 0.7 $M_{\odot}$ we evolve a model every 0.5 $M_{\odot}$. Additionally, we
evolve models over a grid of mixing length parameters from $\alpha_{MLT} = 1.0$
to $\alpha_{MLT} = 2.0$ in steps of 0.1. In addition to the mixing length grid
the evolved grid of models also has dimensions population (A or E) (Table
\ref{tab:comp}) and helium abundance ($Y=0.24, 0.27, 0.3, 0.33, 0.36, 0.39$).
Each model is evolved in DSEP with typical numeric tolerences of one part in
$10^{7}$. Each model is allowed a maximum time step of 50 Myr. 

\begin{table}
  \centering
  \begin{tabular}{c|cc||c|cc}
  \hline
  \hline
  Element & a(X)$_{A}$ & a(X)$_{E}$ & Element & a(X)$_{A}$ & a(X)$_{E}$ \\
  \hline
  Li & -0.08 & --- & In & -1.46 & --- \\
  Be & 0.25 & --- & Sn & -0.22 & --- \\
  B & 1.57 & --- & Sb & -1.25 & --- \\
  C & 6.87 & 5.91 & Te & -0.08 & --- \\
  N & 6.42 & 6.69 & I & -0.71 & --- \\
  O & 7.87 & 6.91 & Xe & -0.02 & --- \\
  F & 3.43 & --- & Cs & -1.18 & --- \\
  Ne & 7.12 & 6.7 & Ba & 1.05 & --- \\
  Na & 5.11 & 5.7 & La & -0.03 & --- \\
  Mg & 6.86 & 6.42 & Ce & 0.45 & --- \\
  Al & 5.21 & 6.61 & Pr & -1.54 & --- \\
  Si & 6.65 & 6.77 & Nd & 0.29 & --- \\
  P & 4.28 & --- & Pm & -99.0 & --- \\
  S & 6.31 & 5.89 & Sm & -1.3 & --- \\
  Cl & -1.13 & 4.37 & Eu & -0.61 & --- \\
  Ar & 5.59 & 5.17 & Gd & -1.19 & --- \\
  K & 3.9 & --- & Tb & -1.96 & --- \\
  Ca & 5.21 & --- & Dy & -1.16 & --- \\
  Sc & 2.02 & --- & Ho & -1.78 & --- \\
  Ti & 3.82 & --- & Er & -1.34 & --- \\
  V & 2.8 & --- & Tm & -2.16 & --- \\
  Cr & 4.51 & --- & Yb & -1.42 & --- \\
  Mn & 4.3 & --- & Lu & -2.16 & --- \\
  Fe & 6.37 & --- & Hf & -1.41 & --- \\
  Co & 3.86 & --- & Ta & -2.38 & --- \\
  Ni & 5.09 & --- & W & -1.41 & --- \\
  Cu & 3.06 & --- & Re & -2.0 & --- \\
  Zn & 2.3 & --- & Os & -0.86 & --- \\
  Ga & 0.78 & --- & Ir & -0.88 & --- \\
  Ge & 1.39 & --- & Pt & -0.64 & --- \\
  As & 0.04 & --- & Au & -1.34 & --- \\
  Se & 1.08 & --- & Hg & -1.09 & --- \\
  Br & 0.28 & --- & Tl & -1.36 & --- \\
  Kr & 0.99 & --- & Pb & -0.51 & --- \\
  Rb & 0.26 & --- & Bi & -1.61 & --- \\
  Sr & 0.61 & --- & Po & -99.0 & --- \\
  Y & 1.08 & --- & At & -99.0 & --- \\
  Zr & 1.45 & --- & Rn & -99.0 & --- \\
  Nb & -0.8 & --- & Fr & -99.0 & --- \\
  Mo & -0.38 & --- & Ra & -99.0 & --- \\
  Tc & -99.0 & --- & Ac & -99.0 & --- \\
  Ru & -0.51 & --- & Th & -2.2 & --- \\
  Rh & -1.35 & --- & Pa & -99.0 & --- \\
  Pd & -0.69 & --- & U & -2.8 & ---
  \end{tabular}
  \caption{Relative Metal composition used where a(H) = 12. Where the relative composition is the the same for both populations A and E it is only listed in the population A colum for the sake of visual clarity.}
  \label{tab:comp}
\end{table}

For each combination of population, $Y$, and $\alpha_{MLT}$ we use the
isochrone generation code first presented in \citet{Dotter2016} to generate a
grid of isochrones. The isochrone generation code identified equivalent
evolutionary points (EEPs) over a series of masses and interpolates between
them. The grid of isochrones generated for this work is avalible as a digital
supplement to this paper. Given the complexity of the parameter space when
fitting multiple populations along with the recent warnings in the liteerature
regarding overfitting datasets \citep[e.g. ][]{Valle2022} we want to develop a
more objective way of fitting isochrones to photometry than if we were to mark
median ridge line positions by hand.

